More than one Author with different Affiliations

### 2016-01-13 manuscript.tex
added table and addressed fig 1 comment

@@

Analyses supported by ANGSD-wrapper are shown in table \X, and a detailed flowchart of each of these workflows is shown in Figure \ref{fig:supp2}, and additional details, documentation, a tutorial, and a wiki can be found on the GitHub page: \url{https://github.com/mojaveazure/angsd-wrapper/wiki}.\jri{add a simple table of all analyses supported.}

@@

In order to use the plotting software, the user navigates to the desired tab and uploads the appropriate file of results. 
The Shiny server automatically parses ANGSD output files and creates the resulting plot(s) (Figure \ref{fig:theta}), which can be saved using the browser's built in image saving capabilities. \jri{is this really chromosome 10 of maize? looks like only first 10Mb. if so, should mention that in figure legend}

\begin{figure}
\centering
\includegraphics[width=130mm]{figures/ThetasPlot.png}
\caption{A visualization of Watterson's $\theta$ estimated by ANGSD across chromosome 10 of {\it Zea mays} spp. {\it mays} using ANGSD-wrapper\label{fig:theta} }
\end{figure}

>>>>

\begin{table}
\begin{center}
    \begin{tabular}{ | l | p{5cm} |}
    \hline
    Methods Implemented & Interactive Graphing \\ \hline
    ABBA BABA & Yes \\ \hline
    Admixture & Yes  \\ \hline
    Ancestral Sequence & N/A \\ \hline
    Genotype Likelihoods & N/A \\ \hline
    Inbreeding Coefficients & N/A \\ \hline
    PCA & Yes \\ \hline
    Site Frequency Spectrum & Yes \\ \hline
    Theta Calculation & Yes \\ \hline
    \end{tabular}
    \caption{Table of methods implemented in ANGSD-wrapper}
    \label{tab:methods}
    \end{center}
\end{table}

@@

Analyses supported by ANGSD-wrapper are shown in table \ref{tab:methods}, and a detailed flowchart of each of these workflows is shown in Figure \ref{fig:supp2}, and additional details, documentation, a tutorial, and a wiki can be found on the GitHub page: \url{https://github.com/mojaveazure/angsd-wrapper/wiki}.

@@

In order to use the plotting software, the user navigates to the desired tab and uploads the appropriate file of results. 
The Shiny server automatically parses ANGSD output files and creates the resulting plot(s) (Figure \ref{fig:theta}), which can be saved using the browser's built in image saving capabilities.

\begin{figure}
\centering
\includegraphics[width=130mm]{figures/ThetasPlot.png}
\caption{A visualization of Watterson's $\theta$ estimated by ANGSD across the first 10 megabases of chromosome 10 in {\it Zea mays} spp. {\it mays} using ANGSD-wrapper\label{fig:theta} }
\end{figure}
